\vspace{-1cm} \normalsize Supplementary Information\\\vspace{0.2cm} \LARGE Basic aspects of species' distributions

### 2021-05-31 manuscript/supplementary_information.tex
Finished methods section
New version of the draft

% Full description of Binomial model with multiple environmental covariates
% Full description of Categorical model with multiple environmental covariates
% Using a MMSBM to calculate species similarity
% Edge problem in stan and need to define minimum probability.

@@

@@

>>>>

% Full description of Binomial model with multiple environmental covariates
% Full description of Categorical model with multiple environmental covariates
% Full description of Categorical model with heavy-tails---generalized error distribution
% Full description of Categorical model with heavy-tails---Student's t-distribution
% Full description of Categorical model with skewed---skewed normal distribution
% Using a MMSBM to calculate species similarity
% Edge problem in stan and need to define minimum probability.

@@

\subsubsection*{Alternative variance-covariance structures}
The model structure defined above allows us to test how different sources of information characterize each of the different parameters. Specifically, we can do this by modifying Eq.~(\ref{eq:covariance-baseline}). For example, imagine that we have multiple matrices $D^k$ characterizing species' differences along different axis of variation---e.g.~two matrices characterizing physiological and environmental traits. One can modify Eq.~(\ref{eq:covariance-baseline}) for a particular parameter---e.g.~$\beta_{i}$---such that
\begin{equation} 
\Sigma_{ij} = \eta\,\text{exp}\left(-\sum_k\rho_{k} {D^{k}_{ij}}^2\right) + \delta_{ij} \sigma ,
\label{eq:covariance-complex}
\end{equation}
where now $\rho_{k}$ are separate relevance hyperparameters for each distance matrix in the total variance of $\beta_i$.

@@

\begin{figure}[ht]
  \centering
    \includegraphics[width=0.9\textwidth]{figures/means-Rapopor}
    	  \vspace{0.1cm}
	   \caption{Universality of the relationship between mean and variance of species' distributions. Comparison between how different types of species are mapped in Fig.~\ref{fig:correlation}a. Panel (a) describes the correlation coefficient between $\beta_i$ and $\gamma_i$ for each type of species. Panel (b) shows the differences between neophytes and native species in the way these are distributed along the environmental gradient. Panel (c) shows the same differences for species that have decreased, decreased in low elevations, increase and remain stable over the last decades (see Supplementary Table 1 for further details).}
	   %7.5-4
      \label{sfig:universality}
\end{figure}
